Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-15 paper/main.tex
new files added

\usepackage{amsmath,amssymb}
%\usepackage[square,numbers,sort&compress]{natbib}
\usepackage{xspace}
%% Useful packages
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage{multirow}
\usepackage{booktabs} % For formal tables
\usepackage{enumitem}
\usepackage{afterpage}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[square,numbers,sort]{natbib}
% Fixes for using natbib and llncs
\makeatletter
% required for natbib to have "References" printed and as section*, not chapter*
\renewcommand\bibsection%
{\section*{\refname\@mkboth{\MakeUppercase{\refname}}{\MakeUppercase{\refname}}}}
\renewcommand\@biblabel[1]{#1.}
\def\bibfont{\small}
\makeatother

@@

>>>>

\usepackage{amsmath,amssymb}
%\usepackage[square,numbers,sort&compress]{natbib}
\usepackage{xspace}
%% Useful packages
\usepackage{graphicx}
\usepackage{pdflscape,adjustbox}
\usepackage{multirow}
\usepackage{booktabs} % For formal tables
\usepackage{enumitem}
\usepackage{afterpage,tabularx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[square,numbers,sort]{natbib}
% Fixes for using natbib and llncs
\makeatletter
% required for natbib to have "References" printed and as section*, not chapter*
\renewcommand\bibsection%
{\section*{\refname\@mkboth{\MakeUppercase{\refname}}{\MakeUppercase{\refname}}}}
\renewcommand\@biblabel[1]{#1.}
\def\bibfont{\small}
\makeatother

@@

Table~\ref{tab:results} shows

\begin{adjustbox}{angle=90}
\begin{tabular}{lllrrrrrrr}
\toprule
{} & Problem &                instance &  Fitness\_CEGO\_mean &  Fitness\_CEGO\_std &  Fitness\_UMM\_mean &  Fitness\_UMM\_std &  Improvement &  ttest statistic &  ttest pvalue \\
\midrule
0  &     LOP &  lop/RandA1/N-t1d100.01 &            78696.6 &        811.368145 &           76119.6 &       915.392836 &     0.032746 &         6.662091 &  2.989433e-06 \\
1  &     LOP &  lop/RandA1/N-t1d100.02 &            79686.5 &        367.876262 &           76827.7 &       890.969391 &     0.035876 &         9.378614 &  2.374606e-08 \\
2  &     LOP &  lop/RandA1/N-t1d150.01 &           187605.5 &       1906.941953 &          179508.3 &      1647.878437 &     0.043161 &        10.159726 &  6.994357e-09 \\
3  &     LOP &  lop/RandA1/N-t1d150.02 &           184320.9 &        973.457920 &          177592.8 &      1196.159298 &     0.036502 &        13.795848 &  5.183671e-11 \\
4  &     LOP &  lop/RandA1/N-t1d200.01 &           335391.1 &       2288.960096 &          323513.6 &      1371.235712 &     0.035414 &        14.076557 &  3.714220e-11 \\
5  &     LOP &  lop/RandA1/N-t1d200.02 &           333149.5 &       2497.207474 &          319675.8 &      2242.631629 &     0.040443 &        12.694417 &  2.029610e-10 \\
6  &     LOP &  lop/RandA2/N-t2d150.01 &            24682.7 &        976.639596 &           15297.7 &       563.527787 &     0.380226 &        26.320561 &  8.038269e-16 \\
7  &     LOP &  lop/RandA2/N-t2d150.02 &            24250.8 &       1354.897110 &           14724.9 &       667.454276 &     0.392808 &        19.944373 &  1.010663e-13 \\
8  &    PFSP &          pfsp/rec05.txt &             1317.9 &         25.075220 &            1330.7 &        17.901272 &    -0.009712 &        -1.313790 &  2.054160e-01 \\
9  &    PFSP &          pfsp/rec13.txt &             2128.2 &         24.965754 &            2158.7 &        29.533597 &    -0.014331 &        -2.494040 &  2.258601e-02 \\
10 &    PFSP &          pfsp/rec19.txt &             2398.6 &         19.839355 &            2405.1 &        12.582616 &    -0.002710 &        -0.874932 &  3.931359e-01 \\
11 &     QAP &           qap/kra32.dat &           115907.0 &       4663.427566 &          116320.0 &      4673.468852 &    -0.003563 &        -0.197816 &  8.454055e-01 \\
12 &     QAP &           qap/nug12.dat &              624.2 &         26.288147 &             660.4 &        17.276831 &    -0.057994 &        -3.639054 &  1.876810e-03 \\
13 &     QAP &           qap/nug30.dat &             7486.8 &         40.411220 &            7474.0 &        83.910005 &     0.001710 &         0.434612 &  6.690098e-01 \\
14 &     QAP &           qap/tho30.dat &           192416.0 &       2584.174401 &          191482.0 &      4419.722264 &     0.004854 &         0.576896 &  5.711548e-01 \\
\bottomrule
\end{tabular}
\end{adjustbox}
